oREVIRT analysis

### 2022-11-08 analysis/irt_analysis.Rmd
update

rasch_selected_items <- readRDS("../saves/rasch_selected_items.rds")

@@

ggplot(params_sex_p, aes(x = sex_dif, label = item, y = reorder(item, abs(sex_dif)), col = ex))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(alpha = .5)+
  scale_color_manual(values = c("black", "firebrick"))+
  guides(col = "none")+
  labs(x = "Difference between estimates (female - male)", y = "Target word")+
  theme_few()
```

>>>>

rasch_selected_items <- readRDS("../saves/selected_items_rasch.rds")

@@

ggplot(params_sex_p, aes(x = sex_dif, label = item, y = reorder(item, abs(sex_dif)), col = ex))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(alpha = .5)+
  scale_color_manual(values = c("black", "firebrick"))+
  guides(col = "none")+
  labs(x = "DIF: Difference between estimates (female - male)", y = "Target word")+
  theme_few()
```

```{r}
ggsave("../graphs/dif.png", height = 12, width = 8, scale = 1)
```
